Implicit yaddayadda

### 2011-10-26 papers/PLDI2012/implicitization.tex
ajout d'une option au package siunitx pour que ca compile avec la version 2 du package
on force siunitx a la version 1 avec une option speciale
siunitx
Utilisons dcolumn au lieu de siunitx!

\usepackage{siunitx}

@@

\begin{table*}
\begin{center}
\setlength{\tabcolsep}{1ex}
\begin{tabular}{|l
|S[tabnumalign=right,tabformat=2.2]S[tabnumalign=right,tabformat=1.2]S[tabnumalign=right,tabformat=1.2]%
|S[tabnumalign=right,tabformat=2.2]S[tabnumalign=right,tabformat=1.2]S[tabnumalign=right,tabformat=1.2]%
|S[tabnumalign=right,tabformat=2.2]S[tabnumalign=right,tabformat=1.2]S[tabnumalign=right,tabformat=1.2]%
|S[tabnumalign=right,tabformat=2.2]S[tabnumalign=right,tabformat=1.2]S[tabnumalign=right,tabformat=1.2]%
|S[tabnumalign=right,tabformat=2.2]S[tabnumalign=right,tabformat=1.2]S[tabnumalign=right,tabformat=1.2]|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{G/S}}
& \multicolumn{3}{c|}{\textbf{PF/S}}
& \multicolumn{3}{c|}{\textbf{PF/G}}
& \multicolumn{3}{c|}{\textbf{G+PF/PF}}
& \multicolumn{3}{c|}{\textbf{G+PF/G}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table1}
\end{tabular}
\end{center}
\caption{Result of the comparison of the various techniques described in this
paper: classic Abstract Interpretation (S), \emph{Guided Static Analysis} (G),
\emph{Path-focusing} (PF), and our combined technique (G+PF). For
instance, \textbf{G/S} compares the benefits of \emph{Guided Static Analysis}
over the classic Abstract interpretation algorithm.
The $\subsetneq$ column gives the percentage of invariants more precise (smaller with respect to inclusion) with the left-side technique,
$\supsetneq$ the percentage of invariants better with the right-side technique,
and ``unc.'' gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller.}
% TODO: le reste c'est quand c'est egal?
\label{tab:techniques}
\end{table*}

>>>>

\usepackage{dcolumn}

@@

\begin{table*}
\begin{center}
\setlength{\tabcolsep}{1ex}
\begin{tabular}{|l
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}%
|D{.}{.}{2}D{.}{.}{2}D{.}{.}{2}|} \hline
\multicolumn{1}{|c|}{\textbf{Benchmark}}
& \multicolumn{3}{c|}{\textbf{G/S}}
& \multicolumn{3}{c|}{\textbf{PF/S}}
& \multicolumn{3}{c|}{\textbf{PF/G}}
& \multicolumn{3}{c|}{\textbf{G+PF/PF}}
& \multicolumn{3}{c|}{\textbf{G+PF/G}} \\ %\cline{2-16}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.}
& \multicolumn{1}{c}{$\subsetneq$} & \multicolumn{1}{c}{$\supsetneq$} & \multicolumn{1}{c|}{unc.} \\
 \hline
 \input{table1}
\end{tabular}
\end{center}
\caption{Result of the comparison of the various techniques described in this
paper: classic Abstract Interpretation (S), \emph{Guided Static Analysis} (G),
\emph{Path-focusing} (PF), and our combined technique (G+PF). For
instance, \textbf{G/S} compares the benefits of \emph{Guided Static Analysis}
over the classic Abstract interpretation algorithm.
The $\subsetneq$ column gives the percentage of invariants more precise (smaller with respect to inclusion) with the left-side technique,
$\supsetneq$ the percentage of invariants better with the right-side technique,
and ``unc.'' gives the percentage of invariants that are uncomparable, i.e
neither greater nor smaller.}
% TODO: le reste c'est quand c'est egal?
\label{tab:techniques}
\end{table*}
